% resume, by Katherine Erickson

\documentclass{article}
\usepackage{enumitem}
\usepackage[margin=.75in]{geometry}
\usepackage{multicol}
\setlength\parindent{0pt}

\date{\today}

\newcommand{\name}{Katherine Erickson}
\newcommand{\address}{669 Degraw Street, Apt. 3\\Brooklyn, NY, 11217}
\newcommand{\phone}{218-349-8150}
\newcommand{\email}{katherine.erickson@gmail.com}
\newcommand{\website}{katherineerickson.com}

\newcommand{\header}{
	\begin{minipage}[t]{.5\textwidth}
		\Huge
			\name
		\normalsize
			\vspace{1em}\\
			\website \\

	\end{minipage}
	\begin{minipage}[t]{.5\textwidth}
		\vspace{-1.6em}
		\begin{flushright}
			\footnotesize
				\address \\
				\phone \\
				\email \\
			\normalsize
		\end{flushright}
	\end{minipage}
}

\begin{document}
	\header

	\section*{Education}
	\begin{description}
		\item[M.S. in Computer Science] New York University, current, 4.0 GPA
		\item[B.A.] Oberlin College, 2006, Biology and Cinema Studies majors, Chemistry minor, 3.88 GPA
		\footnotesize
		\setitemize[0]{leftmargin=0pt,itemindent=10pt}
		\begin{itemize}
			\item Highest Honors in Biology
			\item Phi Beta Kappa (2006) and Sigma Xi (2005)
			\item Merit Scholarships: John Oberlin, Robert B. and Sophia Whiteside, National Merit 
			\item Biology Prizes: Leo S. Millar (2006), Hope Hibbard (2005), Florence Burger (2005-2006)
		\end{itemize}
		\normalsize
		\item[H.S. Diploma] East High School, Duluth, MN, 2002, 4.0 GPA, Valedictorian (shared)
		\item[GRE] 2011, Quantitative 800/800, Verbal 780/800, Analytical Writing 5.5/6
	\end{description}
    
	\section*{Employment}
	\begin{description}
		\item[Assistant Research Scientist (and Software Developer)]
		\emph{Labs of Dr. Fabio Piano and Dr. Kris Gunsalus,
			Center for Genomics and Systems Biology,
			New York University
			(research: 2009-present; software: 2013-present)
		}

		Designed databases and built web interfaces to store, present, 
		and navigate data for various research projects.
		Developed and implemented tools for lab organization.
		Examples at katherineerickson.com.
		
		Assisted on genome-scale screen using pairwise gene knockdowns to uncover
		genetic interactions in \emph{Caenorhabditis elegans} early embrygenesis. 
		Contributed to experiment design, organization, and analysis.

		\item[Client Service Coordinator]
		\emph{H\&R Block, Washington, DC (2009)}
			
		Processed tax returns, managed appointments, answered 6 phone lines, 
		trained new employees, and responded to clients' questions and concerns.
		Earned tax preparation certificate (72 hours coursework).

		\item[Deli Manager and Cook]
		\emph{Sticky Fingers Bakery, Washington, DC (2007-2008)}
		
		Managed deli production, developed recipes, ordered produce,
		and cooked at an all-vegan bakery.

		\item[Research Technician and Assistant]
		\emph{Lab of Dr. Taylor Allen,
			Oberlin College Biology Department (2005-2007)
		}
		
		Mapped and characterized suppressor mutations to reveal interactions 
		within and between muscle proteins in \emph{C. elegans}.
		Wrote honors thesis about the project, 
		and presented findings at international scientific meetings.

		Recruited and advised participants for study about oxygen
		consumption fluctuation over the menstrual cycle.

		\item[Prior Job Experience]
		Support Staff at home for women with schizophrenia.
		Dietary Aide and dishwasher at assisted living home.
		Many years of early morning newspaper delivery.
	\end{description}

	\section*{Programming}
	\begin{description}
			\item[Skills] Python, Django, MySQL, database design, C, Java, HTML, CSS, \LaTeX, git (all experience in OS X or Linux)
			\item[Dabblings] jQuery (JavaScript), R, ML, PHP-based web development
			\item[Web Development] Please see portfolio at katherineerickson.com, code at github.com/katur.
			\item[Coursework] Master's-level NYU courses taken:
				\footnotesize
				\begin{itemize}
				\begin{multicols}{3}
					\item Advanced Database Systems
					\item Programming Languages
					\item Operating Systems
					\item Database Systems
					\item Fundamental Algorithms
					\item Discrete Math
					\item Applied Genomics
					\item PACII (Computer Organization)
					\item PACI (Java, Data Structuress)
				\end{multicols}
				\end{itemize}
				\normalsize
	\end{description}
			
	\section*{Other Experiences}
	\begin{description}
			\item[Bicycle Touring] Organized and conducted tours from
			Portland to San Francisco (2011, 13 days), 
			coast-to-coast across the Southern United States (2008, 49 days),
			along the Mississippi River (2007, 25 days), and
			circumnavigating Lake Superior (2003, 14 days).
					
			\item[Steel Drums] \emph{NY Pan Sonatas (2007-2011) and Oberlin Steel (2003-2007)}

			Competed with 100-member, Brooklyn-based steel drum band in 
			annual NYC Panorama competition (3 wins).
			Played and toured with Oberlin's student-run steel drum band.
			Taught and organized a steel drum course for college and high 
			school students in Oberlin's Experimental College Program.
			
			\item[Food Coops and Community Gardens] 
			\emph{Park Slope Food Coop (2010-present), 
				Fort Totten DC Community Garden (2008-2009),
				Oberlin Student Cooperative Organization (2002-2006)
			}

			Notable experiences in the Oberlin coops:
			Discussion and Communications Coordinator 
			(mediating large-group discussions and running management team meetings);
			treasurer; bread baker; pizza maker; 
			four years in the notorious vegan, no-sugar, at-least-half-whole-wheat coop.
	\end{description} 
			
	\section*{Publications, Abstracts, Presentations}
	\begin{itemize}
			\item White AG, Lees B, Kao HL, Cipriani PG, Munarriz E, Paaby A, Erickson K, Guzman S, 
			Rattanakorn K, Sontag E, Geiger D, Gunsalus KC, Piano F.
			DevStaR: High-throughput quantification of \emph{C. elegans} developmental stages, IEEE TMI, 2013.
			\item 16th International \emph{C. elegans} Meeting, UCLA, June 2007. 
			Abstract/Poster: ``Reversion Analysis with \emph{unc-54} and \emph{unc-90} Mutants Reveals Paths of Communication within Myosin and within Its Regulatory System.''
			\item 51st Annual Biophysical Society Meeting, Baltimore, March 2007.
			Abstract/Poster: ``Communication within Myosin and between It and Troponin.''
			\item Undergraduate Honors Thesis and Presentation: ``Interactions Made by Myosin and by Troponin-T: Genetic Suppressor Analysis,'' 2006.
			\item 50th Annual Biophysical Society Meeting, Salt Lake City, March 2006.
			Abstract/Poster: ``Interactions Made by Myosin and by Troponin-T: Genetic Suppressor Analysis.''
			\item 15th International \emph{C. elegans} Meeting, UCLA, June 2005.
			Abstracts/Posters: ``Novel Domains of the Muscle Regulatory Protein Troponin-T and Their Roles'' and 
			``Design and Efficacy of Two Investigative, Physiological Projects Using \emph{C. elegans}.''
	\end{itemize}
\end{document}
